Predicting sales of newly published books

### 2015-08-25 paper.tex
arreglando una traducción de términos

\begin{minipage}{2.3in} \begin{verbatim}
REST OF DISTRIBUTED FIRST YEAR
REPRINTS
NUMBER OF REPRINTS
TOTAL DEVOLUTIONS
MALLS DEVOLUTIONS
DELEGATES DEVOLUTIONS
REST OF DEVOLUTIONS
TOTAL DEVOLUTIONS FIRT YEAR
MALLS DEVOLUTIONS FIRST YEAR
DELEGATES DEVOLUTIONS FIRST YEAR
REST OF DEVOLUTIONS FIRST YEAR
GIFTS
UNITS DISTRIBUTED IN FIRST EDITION
TOTAL SELLING POINTS
MALLS SELLING POINTS
DELEGATES SELLING POINTS
REST OF SELLING POINTS
TOTAL SELLING POINTS FIRST YEAR
MALLS SELLING POINTS FIRST YEAR
DELEGATES SELLING POINTS FIRST YEAR
REST OF SELLING POINTS FIRST YEAR
WEEKS ON SALE
POSITIVE SALE MARKET
MEDIUM SALE MARKET
NEGATIVE SALE MARKET
\end{verbatim} \end{minipage}    \\

@@

\begin{minipage}{2.3in} \begin{verbatim}
MALLS SALES
TOTAL DISTRIBUTED FIRST YEAR
TOTAL SELLING POINTS
MALLS DISTRIBUTED
DELEGATES DISTRIBUTED FIRST YEAR
MALLS SELLING POINTS
TOTAL SALES FIRST YEAR
MEDIUM SALE MARKET
WEEKS ON SALE
DELEGATES DISTRIBUTED
AUTHOR
DELEGATES SALES FIRST YEAR
GIFTS
MALLS DEVOLUTIONS FIRST YEAR
DELEGATES SALES
REST OF DISTRIBUTED
DELEGATES DEVOLUTIONS FIRST YEAR
TOTAL DISTRIBUTED
REST OF DEVOLUTIONS FIRST YEAR
RETAIL PRICE
TOTAL SALES (output)
\end{verbatim} \end{minipage}    \\

@@

\begin{minipage}{2.3in} \begin{verbatim}
TOTAL DEVOLUTIONS
REPRINTS
TOTAL SELLING POINTS FIRST YEAR
UNITS DISTRIBUTED IN FIRST EDITION
NUMBER OF REPRINTS
TOTAL DEVOLUTIONS FIRT YEAR
TOTAL DISTRIBUTED FIRST YEAR
TOTAL SELLING POINTS
WEEKS ON SALE
TOTAL DISTRIBUTED
RETAIL PRICE
PRINT-RUN
TOTAL SALES (output)
\end{verbatim} \end{minipage}     \\

@@

Finally, after analyzing the dataset with 13 descriptive inputs per %FERGU: describis los resultados antes de explicar que volveis a hacer SOM
book, and paying attention to the company experienced manager's
recommendations, 7 inputs were considered; specifically, variables
\emph{EDITORIAL} and \emph{SUBJECT} were included, while %FERGU: vale, no useis SUBJECT, usad mejor SUBJECT (SUBJECT es materia de física, creo xD).    ok, ¡gracias!
\emph{TOTAL DEVOLUTIONS, REPRINTS, TOTAL SELLING POINTS FIRST YEAR,
  NUMBER OF REPRINTS, TOTAL DEVOLUTIONS FIRT YEAR, TOTAL DISTRIBUTED FIRST YEAR,
  WEEKS ON SALE, PRINT-RUN} were discarded.  
	% Hay que aportar datos de por qué se hizo esto. ¿Análisis de planos?
	% ¿Análisis de varianza? - jj
	% [Pedro] En cuanto estén los SOM definitivos lo añadimos. Está relacionado con el ISSUE #6
Figure \ref{fig:som13} shows the initial analysis of dataset using the SOM on 
the total of 13 descriptive inputs per book.
This, along with the expert manager knowledge determined the final 7 inputs 
to be considered.
Table \ref{tabla:params7} shows the final set of variables describing a book, 
taking into account the company experienced manager knowledge.

>>>>

\begin{minipage}{2.3in} \begin{verbatim}
REST OF DISTRIBUTED FIRST YEAR
REPRINTS
NUMBER OF REPRINTS
TOTAL DEVOLUTIONS
MALLS DEVOLUTIONS
DELEGATES DEVOLUTIONS
REST OF DEVOLUTIONS
TOTAL DEVOLUTIONS FIRT YEAR
MALLS DEVOLUTIONS FIRST YEAR
DELEGATES DEVOLUTIONS FIRST YEAR
REST OF DEVOLUTIONS FIRST YEAR
GIFTS
UNITS DISTRIBUTED IN FIRST EDITION
TOTAL SELLING POINTS
MALLS SELLING POINTS
DELEGATES SELLING POINTS
REST OF SELLING POINTS
TOTAL SELLING POINTS FIRST YEAR
MALLS SELLING POINTS FIRST YEAR
DELEGATES SELLING POINTS FIRST YEAR
REST OF SELLING POINTS FIRST YEAR
WEEKS FOR SALE
POSITIVE SALE MARKET
MEDIUM SALE MARKET
NEGATIVE SALE MARKET
\end{verbatim} \end{minipage}    \\

@@

\begin{minipage}{2.3in} \begin{verbatim}
MALLS SALES
TOTAL DISTRIBUTED FIRST YEAR
TOTAL SELLING POINTS
MALLS DISTRIBUTED
DELEGATES DISTRIBUTED FIRST YEAR
MALLS SELLING POINTS
TOTAL SALES FIRST YEAR
MEDIUM SALE MARKET
WEEKS FOR SALE
DELEGATES DISTRIBUTED
AUTHOR
DELEGATES SALES FIRST YEAR
GIFTS
MALLS DEVOLUTIONS FIRST YEAR
DELEGATES SALES
REST OF DISTRIBUTED
DELEGATES DEVOLUTIONS FIRST YEAR
TOTAL DISTRIBUTED
REST OF DEVOLUTIONS FIRST YEAR
RETAIL PRICE
TOTAL SALES (output)
\end{verbatim} \end{minipage}    \\

@@

\begin{minipage}{2.3in} \begin{verbatim}
TOTAL DEVOLUTIONS
REPRINTS
TOTAL SELLING POINTS FIRST YEAR
UNITS DISTRIBUTED IN FIRST EDITION
NUMBER OF REPRINTS
TOTAL DEVOLUTIONS FIRT YEAR
TOTAL DISTRIBUTED FIRST YEAR
TOTAL SELLING POINTS
WEEKS FOR SALE
TOTAL DISTRIBUTED
RETAIL PRICE
PRINT-RUN
TOTAL SALES (output)
\end{verbatim} \end{minipage}     \\

@@

Finally, after analyzing the dataset with 13 descriptive inputs per %FERGU: describis los resultados antes de explicar que volveis a hacer SOM
book, and paying attention to the company experienced manager's
recommendations, 7 inputs were considered; specifically, variables
\emph{EDITORIAL} and \emph{SUBJECT} were included, while %FERGU: vale, no useis SUBJECT, usad mejor SUBJECT (SUBJECT es materia de física, creo xD).    ok, ¡gracias!
\emph{TOTAL DEVOLUTIONS, REPRINTS, TOTAL SELLING POINTS FIRST YEAR,
  NUMBER OF REPRINTS, TOTAL DEVOLUTIONS FIRT YEAR, TOTAL DISTRIBUTED FIRST YEAR,
  WEEKS FOR SALE, PRINT-RUN} were discarded.  
	% Hay que aportar datos de por qué se hizo esto. ¿Análisis de planos?
	% ¿Análisis de varianza? - jj
	% [Pedro] En cuanto estén los SOM definitivos lo añadimos. Está relacionado con el ISSUE #6
Figure \ref{fig:som13} shows the initial analysis of dataset using the SOM on 
the total of 13 descriptive inputs per book.
This, along with the expert manager knowledge determined the final 7 inputs 
to be considered.
Table \ref{tabla:params7} shows the final set of variables describing a book, 
taking into account the company experienced manager knowledge.
